MSHS COVID-19 Vaccination Summary

### 2023-07-24 MSHS Vaccines Administered Hybrid Data Model.Rmd
Clean up if-else statement when repo is not updated.
Update repository and associated codes to use latest data pull from Epic for all vaccines administered from 01-2022 to 06-2023 with all relevant immunization names.

# Import reference data for site and pod mappings
# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(
  user_directory,
  "/Hybrid Sched & Admin Reporting",
  "/Hybrid Reporting Dept Mapping 2022-10-27.xlsx"),
  sheet = "Hybrid Dept Mapping")

@@

  # Import schedule repository daily summary for 2020 and 2021
  sched_repo_summary <- readRDS(
    paste0(user_directory,
           "/Hybrid Sched & Admin Reporting",
           "/Hybrid Model Repo",
           "/Sched Arr Visits 2020-2021 Daily Summary 2022-09-14.RDS"))

  # Import vaccine administration repository daily summary for Jan-Jun 2022
  vax_admin_repo_summary <- readRDS(
    paste0(user_directory,
           "/Hybrid Sched & Admin Reporting",
           "/Hybrid Model Repo",
           "/Vaccine Administration Daily Summary 01012022 to 09102022 as of 2022-10-04.RDS"))

@@

  # Save new repository
  saveRDS(hybrid_repo, paste0(user_directory, 
                              "/Hybrid Sched & Admin Reporting",
                              "/Hybrid Model Repo",
                              "/Hybrid Vaccine Admin Data ",
                              format(min(hybrid_repo$Date), "%m%d%y"), " to ",
                              format(max(hybrid_repo$Date), "%m%d%y"),
                              " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
} else {

@@

} else {

>>>>

# Import reference data for site and pod mappings
# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(
  user_directory,
  "HSPI-PM/Operations Analytics and Optimization/",
  "Projects/System Operations/COVID Vaccine",
  "/Hybrid Sched & Admin Reporting",
  "/Hybrid Reporting Dept Mapping 2023-07-24.xlsx"),
  sheet = "Hybrid Dept Mapping")

@@

  # Import schedule repository daily summary for 2020 and 2021
  sched_repo_summary <- readRDS(
    paste0(user_directory,
           "HSPI-PM/Operations Analytics and Optimization",
           "/Projects/System Operations/COVID Vaccine",
           "/Hybrid Sched & Admin Reporting",
           "/Hybrid Model Repo",
           "/Sched Arr Visits 2020-2021 Daily Summary 2022-09-14.RDS"))

  # Import vaccine administration repository daily summary for Jan-Jun 2022
  vax_admin_repo_summary <- readRDS(
    paste0(user_directory,
           "HSPI-PM/Operations Analytics and Optimization",
           "/Projects/System Operations/COVID Vaccine",
           "/Hybrid Sched & Admin Reporting",
           "/Hybrid Model Repo",
           "/Vaccine Administration Daily Summary 01012022 to 06302023 as of 2023-07-24.RDS"))

@@

  # Save new repository
  saveRDS(hybrid_repo, paste0(user_directory, 
                              "HSPI-PM/Operations Analytics and Optimization",
                              "/Projects/System Operations/COVID Vaccine",
                              "/Hybrid Sched & Admin Reporting",
                              "/Hybrid Model Repo",
                              "/Hybrid Vaccine Admin Data ",
                              format(min(hybrid_repo$Date), "%m%d%y"), " to ",
                              format(max(hybrid_repo$Date), "%m%d%y"),
                              " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
} else {

@@
